%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Aryan Samaria}{
\href{mailto:aryansamaria44@gmail.com}{aryansamaria44@gmail.com} | \href{tel:9358737183}{9358737183} \\
Github: \href{https://github.com/aryansamaria}{aryansamaria} | LinkedIn: \href{https://www.linkedin.com/in/aryansamaria}{aryansamaria}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{DATAMONK}
\descript{| PYTHON DEVELOPER }
\location{December 2024 – Present | Jaipur, Rajasthan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Architected a full-stack fintech assistant to answer queries on money transfers and Indian stock market (NSE) data using a modular \textbf{Flask} backend.
\item Implemented a \textbf{Retrieval-Augmented Generation (RAG)} pipeline with \textbf{LlamaIndex} and \textbf{OpenAI} to provide accurate answers from a custom knowledge base.
\item Engineered an end-to-end voice interaction module by integrating \textbf{OpenAI Whisper} for speech-to-text and \textbf{Google TTS} for synthesized audio responses.
\item Developed web scraping scripts using \textbf{BeautifulSoup} to automatically build and update the vector knowledge base from online help articles.
\item Built a dedicated module to fetch, cache, and serve real-time NSE stock data via a REST API, providing information on market movers and company details.
\item Containerized the entire application using \textbf{Docker}, ensuring consistent and reproducible deployment.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Natural Language to SQL Query Assistant}
\descript{| Streamlit Web Application}
\begin{tightemize}
\item Developed an intuitive web application using \textbf{Streamlit} that translates natural language questions into executable SQL queries, allowing non-technical users to query databases.
\item Leveraged \textbf{OpenAI's} language models as the core engine to accurately parse user intent and generate complex, syntactically correct SQL code.
\item Engineered an intelligent data visualization feature that uses \textbf{OpenAI} to analyze query results and automatically generate the most suitable and context-aware chart within the interface.
\end{tightemize}
\sectionsep

\runsubsection{CLICKHOUSE | PERFORMANCE, COMPRESSION EXPLORATION}
\location{July 2025 | Jaipur}
\begin{tightemize}
\item Explored and evaluated ClickHouse, a high-performance columnar database, by designing test tables and running analytical queries to study its architecture and query efficiency.
\item Applied compression codecs like \texttt{Delta}, \texttt{DoubleDelta}, and \texttt{Gorilla} on numeric and time-series data, reducing storage without impacting read performance.
\item Compared disk usage before and after codec application, reducing a table’s size from 8.4 MB to just 44 KB, highlighting ClickHouse’s advanced compression capabilities.
\item Benchmarked ClickHouse against traditional row-based databases by executing aggregation queries, demonstrating faster execution and significantly lower I/O overhead.
\end{tightemize}
\sectionsep


\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{ARYA COLLEGE OF ENGG AND I.T}
\descript{Bachelor of Technology in Artificial Intelligence and Data Science}
\location{May 2024 | Jaipur, Rajasthan}
\location{Cum. GPA: 8.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
Python \textbullet{} SQL \textbullet{} Bash \\
JavaScript (ES6+) \textbullet{} HTML \textbullet{} CSS
\sectionsep

\subsection{Databases \& Query Engines}
PostgreSQL \textbullet{} SQLite \textbullet{} ClickHouse \\
SQL-based Analytics \textbullet{} PostgreSQL Full-Text Search
\sectionsep

\subsection{Frameworks \& Libraries}
Flask \textbullet{} Django \textbullet{} FastAPI \\
Streamlit \textbullet{} LlamaIndex \textbullet{} OpenAI API \\
scikit-learn \textbullet{} Pandas \textbullet{} NumPy \\
BeautifulSoup \textbullet{} REST APIs \textbullet{} Docker \\
Git/GitHub
\sectionsep

\subsection{Machine Learning \& NLP}
Retrieval-Augmented Generation (RAG) \\
Speech-to-Text (Whisper) \textbullet{} Text-to-Speech (Google TTS) \\
Data Preprocessing \textbullet{} Model Deployment \\
Data Visualization \textbullet{} Prompt Engineering
\sectionsep

\subsection{Concepts \& Tools}
Unit Testing (Pytest) \textbullet{} Software Design \\
SQL Optimization \textbullet{} ORM \textbullet{} Linux/UNIX \\
Jupyter Notebook \textbullet{} VSCode
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECH FEST
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tech Fest}
ACEHACK Top 30 team Winner in Rocket Launch technical fes Shankara Global Hackathon. \\
HTL Hackathon NCACSAI 2024 Research Paper on Object detection using ML.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CO-CURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Co-curricular}
Shradhanjali Don-De-Mode Winner. \\
Basketball Runner-up RTU tournament. \\
Fashion Show winner team. \\
Captain Of College Basketball team.
\sectionsep

\end{minipage}
\end{document}